A bayesian method of cosine-based word2vec bias

### 2021-06-10 paperDraft/paperDraft.Rmd

- Even if the difference in means is the same, but the variation is different, the bias metric in the long run could tend toward a different value:

@@

>>>>

- Even if the underlying means are the same, but the variation is different, the bias metric in the long run could tend toward a different value:

@@

- The uncertainty resulting from including the raw datapoint variance into considerations is more extensive than the one suggested by the low p-values obtained from taking means as datapoints.

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
quantile(biasesD2, probs = c(0.275,0.975))
quantile(biasesD1, probs = c(0.275,0.975))
```
\normalsize

### 2021-06-10 paperDraft/paperDraft.tex

\begin{itemize}
\item
  Seemingly high bias measures might arise even if the underlying
  processes actually have the same mean.
\item
  Even if the mean remains the same, non-negligible changes can result
  from a shift in the standard deviation of the original process, and
  the change might go in the opposite direction than a visualisation of
  datapoints might suggest, because with the decrease of standard
  deviation, the factor decreases and the bias increases.
\item
  Even if there is a difference in means, the bias metric can be lower,
  and the uncertainty about it needs to be gauged.
\item
  Even if the difference in means is the same, but the variation is
  different, the bias metric in the long run could tend toward a
  different value:
\end{itemize}

@@

>>>>

\begin{itemize}
\item
  Seemingly high bias measures might arise even if the underlying
  processes actually have the same mean.
\item
  Even if the mean remains the same, non-negligible changes can result
  from a shift in the standard deviation of the original process, and
  the change might go in the opposite direction than a visualisation of
  datapoints might suggest, because with the decrease of standard
  deviation, the factor decreases and the bias increases.
\item
  Even if the underlying means are the same, but the variation is
  different, the bias metric in the long run could tend toward a
  different value:
\end{itemize}

@@

\begin{itemize}
\item
  Even if there is a difference in means, the bias metric can be lower,
  and the uncertainty about it needs to be gauged.
\item
  The uncertainty resulting from including the raw datapoint variance
  into considerations is more extensive than the one suggested by the
  low p-values obtained from taking means as datapoints.
\end{itemize}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{quantile}\NormalTok{(biasesD2, }\DataTypeTok{probs =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.275}\NormalTok{,}\FloatTok{0.975}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##    27.5%    97.5% 
## 1.539149 2.166488
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{quantile}\NormalTok{(biasesD1, }\DataTypeTok{probs =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.275}\NormalTok{,}\FloatTok{0.975}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##    27.5%    97.5% 
## 1.300648 2.356815
\end{verbatim}
